---
title: "linear_models"
author: "Matthew Lawlor"
date: "12/3/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

## Import data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars , y = price, color = borough)) +
  geom_point()
```

Let's fit the model we care about

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's look at the result...
note: these are not very practical
```{r, include = FALSE}
fit
summary(fit)
summary(fit)$coef ##this is a matrix
coef(fit) ##this is a vector
fitted.values(fit)
residuals(fit)
```

Let's look a the result better...

```{r}
broom::glance(fit)

broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable()
```

## Be in control of factors

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

Look at that plot again

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars , y = price, color = borough)) +
  geom_point()
```

and that model

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
```

## Diagnostics

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)
```

## Hypothesis tests

This does t-tests by default
```{r}
fit %>% 
  broom::tidy()
```

What about the significance of `borough` as a variable (ie F test)

```{r}
fit_null = lm(price ~ stars, data=nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data=nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```


## Nest data, fit models

This is formal and complex

```{r}
fit = lm(price ~ stars * borough + room_type * borough, data=nyc_airbnb)

broom::tidy(fit)
```

This is more exploratory but maybe easier to understand

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  )
```



